---
title: "R Tutorial Day 2"
output: html_notebook
---


To Create new chunk use: Ctrl + Alt + I


To run the current chunk use: Ctrl + Shift + Enter  
```{r}
print("this is test!!")
print("Hello World")
```
To Run single code of line use: Ctrl + Enter
```{r}
print("Hello world")
```
```{r}
10 + 5 

```


### we can use = or <- as assignment operator in R 

```{r}
x <- 10
y <- 20

z <- x + y
z
```
### We can check what is the type of the given data/variable using: typeof()

```{r}
typeof(19)
typeof(12.3)
typeof("ajay")
typeof(T)
typeof(30L)

```
### We can also use: class() 

```{r}
class(19)
class(17.8)
class("ajay")
class(F)
class(50L)
```
### We can also use: str()

```{r}
str(18)
str(34.45)
str("ajay")
str(T)
```

# Data Structures

## Vectors:  by using: variable_name <- c(value1, value2, value3, ....)
* note 1: values in Vector are homogeneuous meaning they should be of same type.
* note 2: we can use ('ajay', 10, 23.4, TRUE) but these values will be considered as string type.
```{r}
ages <- c(18,19,20,27,35,29)
ages
```
### Accessing the index/value from vector:
```{r}
ages[1]
ages[2]
ages[3]
ages[4]
ages[5]
ages[6]
ages[7] # note here this index was out of range, hence it gave output as NA
```
### Slicing in vectors

```{r}
info
info[1:3]
info[1:4]
info[1:5]
```

### Accessing element of from particular index:
```{r}
info
info[c(1,4)]
```


## To know at which location our element is present use match(element, iterator_name) :-

```{r}
colors <- c("red", "yellow", "green", "blue")
colors

match("green", colors)
```

## replace element in a vector:

```{r}
colors[2] <- "black"
colors
```

```{r}
num <- c(10,20,30,60,50)
num

match(60, num)

num[4] <- 40
num
```
```{r}
num[1:3] <- c(1,2,3)
num
```
```{r}
num[1:3] <- c(10,20,30)
num
```
```{r}
num[c(1,4)] <- c(1,4)
num
```

```{r}
num[2:3] <- c(2,3)
num[5] <- 5
num
```

## list:

``` if you want to create a list use var <- list(value1, value2 ,....) ```

```{r}
lst <- list("ajay",list("a","b"), 100, 15.3, TRUE)
lst
```

```{r}
lst[1] <- "vijay"
lst
```



## Data Frame:


```{r}
ID <- c(101,102,103,104)
Name <- c("A", "B", "c", "D")
Age <- c(24,23,26,25)
Dept <- c("HR","scientist", "Analyst", "IT")
```

```{r}
df <- data.frame(ID, Name, Age, Dept)
df
```

```{r}
view(df)
```

```{r}
df[2,2]
```


```{r}
df[2,1:3]
```



```{r}
df[1, c(2,4)]
```

```{r}
df[1:3,4]
```

```{r}
df[3,2] <- "C"
df
```




